Topological approach to finding blackholes in directed networks

### 2019-12-02 blackholes/pavt/article.tex
Algorithm design in general

%
\section{Graph perprocessing}
%

%
\section{Graph topology}
%

%
\section{Algorithm design}
%

>>>>

%
\section{Algorithm design}
We propose to look at the black hole search task from the following perspective: it would be divided into two independent 
tasks. 
The first one is graph preprocessing. Here we aim to simplify graph structure as far as it is possible with respect to
restricted time span. Decreased graph scale would definitely speed up the rest of the calculation, as it is result in brute force search in most cases.
The second is the blackhole search itself. This step is done after preprocessing and the goal here is to find as many blackholes as possible in restricted time.
%

%
\subsection{Graph perprocessing}
%

%
\subsection{Graph topology}
%
